Lensing

### 2015-02-18 Papers/ms.tex
Another paragraph

All such choices involve tradeoffs between convenience and realism.
In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models. Simply parameterized models, such as Sérsic surface
brightness profiles for the source, and SIE models for the lens, are very
convenient. They only have a few adjustable parameters, and they capture
(to ``first order'') relevant prior information that we have about the
source and lens profiles. Of course, they are clearly simplifications,
and can produce misleading results if the actual profile is very different
from any member of the assumed family.

@@

>>>>

All such choices involve tradeoffs between convenience and realism.
Simply parameterized models, such as Sérsic surface
brightness profiles for the source, and SIE models for the lens, are very
convenient. They only have a few adjustable parameters, and they capture
(to ``first order'') relevant prior information that we have about the
source and lens profiles. Of course, they are clearly simplifications,
and can produce misleading results if the actual profile is very different
from any member of the assumed family.

@@

In a previous paper \citep{2011MNRAS.412.2521B} we argued that an ideal
modelling approach lies somewhere between simply-parameterised and
pixellated models. The source and the lens can be built up from a moderate
number of simply parameterised components. For the source, this allows
us to incorporate prior knowledge about the local correlations (the surface
brightness at any particular point is likely to be similar to that at a
nearby point) and the fact that most of the sky is dark. For the lens, if
we are interested in detecting and measuring the properties of dark
substructures, a superposition of an unknown number of ``blobs'' is the
relevant model.
